---
title: "Unsupervised ML"
author: "sourabh jain"
date: "13/11/2020"
output: html_document
---

## Loading and exploring the data
```{r}
data<-read.csv("iris.csv")
dim(data)
summary(data)
library(ggplot2)
ggplot(data,aes(x=SepalLengthCm,y=SepalWidthCm,col=Species))+geom_point()
ggplot(data,aes(x=PetalLengthCm,y=PetalWidthCm,col=Species))+geom_point()
```


## Finding the number of  cluster with Elbow Method
```{r}
data1<-data[,2:5]
tot_wss<-c()
for(i in 1:15)
{
  c1<-kmeans(data1,centers=i)
  tot_wss[i]<-c1$tot.withinss
}
tot_wss

plot(x=1:15, y=tot_wss,type="b",xlab="Number of Clusters",ylab="within groups sum of sqaures")
```

#### From the graph we can observe that as the number of clusters increases, the within groups sum of squares decreases. We take number of clusters as 3 as optimum cluster because it the point where the elbow occurs.

## Applying K means clusters
```{r}
df<-data.frame(x=data$SepalLengthCm,y=data$SepalWidthCm)
kmeansobj<-kmeans(df,centers = 3)
plot(data$SepalLengthCm,data$SepalWidthCm,col=kmeansobj$cluster,pch=19)
points(kmeansobj$centers,col=1:3,pch=4,cex=3,lwd=4)


